Modelling the emergence of whisker barrels

### 2020-07-10 paper/briefpaper/brief.tex
Another tweak of the Fig 4 caption
Changes to Fig 4, a white background for Fig 3.

% This figure is text width
\begin{center}
  \includegraphics[width=\linewidth]{./Fig4.png} \captionof{figure}{
    \MPthreePred{Simulating altered barrel development.  Guidance fields
      (\textbf{A}) and emergent barrel pattern (\textbf{B}) in a Fgf8
      misexpression experiment
      (c.f.~\citealp{assimacopoulos_fibroblast_2012}), simulated by reflecting
      $\rho_1$ from Fig.\,\ref{fig:main}A at the join of the original boundary
      with its mirror. All other model parameters match those in
      Fig.\,\ref{fig:main}C. \textbf{C} Simulating whisker trimming by
      reducing the competitiveness, $\epsilon$, of the one projection. For C3
      only, $\epsilon$ was mutiplied by $m\in(0,1)$. The pattern shown is that
      formed after 30000 steps with $m=0.86$, which reduces the size of the C3
      field to 65\% of its original size, matching the average barrel area
      reduction observed by }
    \citealp{kossut_effects_1992}. \MPthreePred{\textbf{D} The area of the C3
      barrel (black squares) reduces as $m$ is reduced, whereas the mean area of neighbouring
      barrels (B3, C2, C4, D2 \& D3, grey circles) increases. The dotted grey
      line indicates $m=0.86$ for comparison with panel C. If the $\epsilon$
      value is instead reduced for \emph{all} row C projections (including the interstitial
      $\gamma$ projection), the mean row C barrel area is only slightly
      reduced (light grey triangles). In this case, the mean row C area at
      $m=0.86$ is 91\% of that for $m=1$.}}
  \label{fig:fgf8}
\end{center}

@@

\MPthreePred{Although individual whisker trimming reduces barrel size, if an
  entire row is trimmed, barrel sizes for the trimmed row are not obviously
  changed \citep{land_metabolic_1985}. We investigated with a simulation in
  which we varied $\epsilon$ for all of the row C projections.  Although the
  barrels which formed for row C did show some reduction in area
  (Fig.\,\ref{fig:fgf8}D), this reduction was small when compared with the
  individually trimmed C3 simulation. If the effect of trimming any whisker is
  to reduce its $\epsilon$ (the competitiveness of its projection) to 86\% of
  its original value, then the model predicts that the cortical barrels for
  the trimmed C row will retain 91\% of their area.}

@@

Movie corresponding to Fig.\,\ref{fig:main}C in the main paper. Simulation parameters were
\MPtwo{$N=41$, $\alpha=3.6$, $\beta=16.67$, $k=3$, $D=0.5$, $\gamma\in\pm 2$,
$\epsilon=1.2$ and $\delta{t}=0.0001$}. Colours indicate the thalamic
projection for which the connection density is maximal, black lines delineate
boundaries, and overlaid contours show $c>0.5$ \textbf{FIXME: Will need to
  check this statement after regenerating movie}. \cmnt{Barrel labels are
  always located at the centroid of their field(s).} The final frame in the movie
is step 30000 of the simulation.

>>>>

% This figure is text width
\begin{center}
  \includegraphics[width=\linewidth]{./Fig4.png} \captionof{figure}{
    \MPthreePred{Simulating altered barrel development.  Guidance fields
      (\textbf{A}) and emergent barrel pattern (\textbf{B}) in a Fgf8
      misexpression experiment
      (c.f.~\citealp{assimacopoulos_fibroblast_2012}), simulated by reflecting
      $\rho_1$ from Fig.\,\ref{fig:main}A at the join of the original boundary
      with its mirror. All other model parameters match those in
      Fig.\,\ref{fig:main}C. \textbf{C} Simulating whisker trimming by
      reducing the competitiveness, $\epsilon$, of the one projection. For C3
      only, $\epsilon$ was mutiplied by $m\in(0,1)$. The pattern shown is that
      formed after 30000 steps with $m=0.86$, which reduces the size of the C3
      field to 65\% of its original size, matching the average barrel area
      reduction observed by }
    \citealp{kossut_effects_1992}. \MPthreePred{\textbf{D} The area of the C3
      barrel (black squares) reduces as $m$ is reduced, whereas the mean area
      of neighbouring barrels (B3, C2, C4, D2 \& D3, grey circles)
      increases. The dotted grey line indicates $m=0.86$ for comparison with
      panel C. If the $\epsilon$ value is instead reduced for \emph{all} row C
      projections (including the interstitial $\gamma$ projection), the mean
      row C barrel area is only slightly reduced (light grey triangles). In
      this case, the mean area of a simulated row C barrel at $m=0.86$ is 91\%
      of that for $m=1$.}}
  \label{fig:fgf8}
\end{center}

@@

\MPthreePred{Although individual whisker trimming reduces barrel size, if an
  entire row is trimmed, barrel sizes for the trimmed row are not obviously
  changed \citep{land_metabolic_1985}. We investigated with a simulation in
  which we varied $\epsilon$ for all of the row C projections.  Although the
  barrels which formed for row C did show some reduction in area
  (Fig.\,\ref{fig:fgf8}D), this reduction was small when compared with the
  individually trimmed C3 simulation. If the effect of trimming any whisker is
  to reduce its $\epsilon$ (the competitiveness of its projection) to 86\% of
  its original value, then the model predicts that the cortical barrels for
  the trimmed C row will retain 91\% of their area on average.}

@@

Movie corresponding to Fig.\,\ref{fig:main}C in the main paper. Simulation parameters were
\MPtwo{$N=41$, $\alpha=3.6$, $\beta=16.67$, $k=3$, $D=0.5$, $\gamma\in\pm 2$,
$\epsilon=1.2$ and $\delta{t}=0.0001$}. Colours indicate the thalamic
projection for which the connection density is maximal, black lines delineate
boundaries, and overlaid contours show
\cmnt{$c_i > 0.95 \mathrm{max}_i\big(c_i(\mb{x})\big)$. Barrel labels are
  always located at the centroid of their field(s).} The final frame in the movie
is step 30000 of the simulation.
